---
title: "brmsish: random stuff on brms bayesian models"
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![lifecycle](https://lifecycle.r-lib.org/articles/figures/lifecycle-experimental.svg)](https://lifecycle.r-lib.org/articles/stages.html) [![Dependencies](https://tinyverse.netlify.com/badge/brmsish)](https://cran.r-project.org/package=brmsish) [![Project Status: Active  The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active) [![Licence](https://img.shields.io/badge/https://img.shields.io/badge/licence-GPL--2-blue.svg.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html) [![minimal R version](https://img.shields.io/badge/R%3E%3D-`r strsplit(gsub("depends: R \\(|\\)", "", grep("DEPENDS", ignore.case = TRUE, readLines(con = "./DESCRIPTION"), value = TRUE), ignore.case = TRUE), ",")[[1]][1]`-6666ff.svg)](https://cran.r-project.org/)[![packageversion](https://img.shields.io/badge/Package%20version-`r gsub("version: |version:", "", grep("^version", ignore.case = TRUE, readLines(con = "./DESCRIPTION"), value = TRUE), ignore.case = TRUE)`-orange.svg?style=flat-square)](commits/develop)[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master) [![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/brmsish)](https://cran.r-project.org/package=brmsish)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/brmsish)](https://cranlogs.r-pkg.org/badges/grand-total/brmsish)

```{r setup, include = FALSE}

# knitr global options
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  tidy = TRUE
)


```


A poorly documented package with random, tangentially related functions to do visualize or modify [brms](https://paul-buerkner.github.io/brms/index.html) models.

<!-- Unlike other packages for setting up research compendiums, `brmsish` has very simple functionality. Hence, users can focus on the research project itself rather than on learning how to use a new R package. -->

To install the latest developmental version from [github](https://github.com/) you will need the R package [remotes](https://cran.r-project.org/package=remotes) (although it may not install at all):

```{r, eval = FALSE}

# From github
remotes::install_github("maRce10/brmsish")

#load package
library(brmsish)

```

Use it under your own risk. But if you do, please cite [brmsish](https://marce10.github.io/brmsish/) as follows:

Araya-Salas (2022), *brmsish: random stuff on brms bayesian models*. R package version 1.0.0. 


# References

1. Bürkner, P. C. (2017). brms: An R package for Bayesian multilevel models using Stan. Journal of statistical software, 80, 1-28.

1. Bürkner, P. C. (2017). Advanced Bayesian multilevel modeling with the R package brms. arXiv preprint arXiv:1705.11123.

1. Nalborczyk, L., Batailler, C., Lœvenbruck, H., Vilain, A., & Bürkner, P. C. (2019). An introduction to Bayesian multilevel models using brms: A case study of gender effects on vowel variability in standard Indonesian. Journal of Speech, Language, and Hearing Research, 62(5), 1225-1242.

